Self-Supervised Transfer Learning From 2D Images to 3D Point Clouds

### 2022-04-25 doc/paper.tex
updates results

\begin{table*}[t!]
    \centering
    \resizebox{\textwidth}{!}{
        \begin{tabular}{ c | c c c c c c c c c c c c c | c }
                                                   & ceiling        & floor          & wall           & beam           & column         & window         & door           & table          & chair          & sofa           & bookcase       & board          & clutter        & mIOU                   \\
            \hline
            Scratch                                & 90.34          & \textbf{96.84} & 80.63          & 0              & 25.5           & 56.95          & 62.93          & 75.14          & 86.21          & 65.77          & 72.12          & 76.91          & 56.4           & 65.06                  \\
            Supervised                             & \textbf{91.81} & 96.74          & \textbf{84.11} & \textbf{0.21}  & \textbf{34.68} & \textbf{57.64} & \textbf{81.53} & \textbf{77.63} & \textbf{89.82} & \textbf{85.76} & \textbf{76.03} & \textbf{79.27} & \textbf{57.67} & \textbf{70.22} (+5.16) \\
            \hline
            PointContrast                          & 91.97          & \textbf{96.67} & 82.4           & 0              & 17.84          & 56.49          & \textbf{75.39} & \textbf{77.63} & 87.35          & 63.3           & 73.53          & \textbf{79.55} & 58.76          & 66.22 (+1.16)          \\
            PointContrast - Same Scan              & 91.03          & 96.27          & \textbf{82.8}  & 0              & 31.53          & 57.27          & 69.33          & 76.97          & \textbf{88.83} & 45.49          & 71.02          & 77.09          & 57.06          & 64.97 (-0.09)          \\
            PointContrast - 70\% overlap           & 91.85          & 96.56          & 83.55          & 0              & 28.25          & 59.36          & 73.53          & 78.51          & 88.28          & 79.95          & 74.61          & 76             & 61.08          & 68.58 (+3.52)          \\
            Contrastive Scene Contexts             & \textbf{92.34} & 96.02          & 83.53          & 0              & \textbf{40.88} & \textbf{57.73} & 72.11          & 77.5           & 88.15          & \textbf{74.61} & \textbf{74.52} & 76.45          & \textbf{62.64} & \textbf{68.96} (+3.9)  \\
            Contrastive Scene Contexts - Same Scan & 91.68          & 96.59          & 83.21          & 0              & 40.38          & 58.12          & 70.42          & 76.77          & 87.13          & 69.33          & 68.77          & 82.34          & 58.45          & 67.94 (+2.88)          \\
            CME \textbf{(Ours)}                    & 90.8           & 96.57          & 82.52          & \textbf{0.110} & 30.94          & 56.94          & 68.71          & 75.12          & 88.48          & 71.7           & 72.17          & 73.783         & 56.35          & 66.48 (+1.42)          \\
        \end{tabular}
    }
    \caption{S3DIS Semantic Segmentation results (mIOU)}
    \label{table:s3disResults}
\end{table*}

\begin{table*}[t!]
    \centering
    \resizebox{0.8\textwidth}{!}{
        \begin{tabular}{ c | c c c c c c c c c c | c }
                                                   & beam & column        & window        & door & table         & chair         & sofa          & bookcase      & board         & clutter       & mAP@0.5              \\
            \hline
            Scratch                                & 0    & 12.8          & 61.7          & 92.0 & 51.4          & 87.3          & 62.4          & 38.5          & 87.0          & 37.1          & 53.0                 \\
            Supervised                             & 0    & 26.0          & 74.3          & 84.5 & 43.3          & 87.3          & \textbf{81.8} & 37.4          & \textbf{85.4} & \textbf{41.2} & \textbf{56.2} (+3.2) \\
            \hline
            PointContrast                          & 0    & 24.7          & 67.9          & 90.7 & 43.8          & 92.0          & 72.7          & 32.3          & 85.6          & 38.0          & 54.8 (+1.8)          \\
            PointContrast - Same Scan              & 0    & 19.8          & 70.7          & 92.1 & 48.4          & 90.5          & 81.8          & 38.4          & 90.4          & 34.1          & 56.6 (+3.6)          \\
            PointContrast - 70\% overlap           & 0    & 22.6          & 71.6          & 94.6 & 45.8          & 87.9          & 71.7          & 37.0          & 81.0          & 40.9          & 55.3 (+2.3)          \\
            Contrastive Scene Contexts             & 0    & 32.9          & 69.2          & 93.0 & 47.6          & 87.5          & 80.9          & 39.6          & 87.5          & 40.4          & 57.8 (+4.8)          \\
            Contrastive Scene Contexts - Same Scan & 0    & 32.0          & 69.3          & 96.1 & 38.7          & 89.4          & 87.6          & 38.8          & 81.3          & 38.8          & 57.2 (+4.2)          \\
            CME \textbf{(Ours)}                    & 0    & \textbf{35.0} & \textbf{70.0} & 83.4 & \textbf{53.9} & \textbf{88.9} & 71.7          & \textbf{42.2} & 76.1          & 36.7          & 55.8 (+2.8)          \\
        \end{tabular}
    }
    \caption{S3DIS Instance Segmentation Results (mAP@0.5)}
    \label{table:s3disInstanceSegmention}
\end{table*}

@@

\begin{table*}[t!]
    \centering
    \resizebox{\textwidth}{!}{
        \begin{tabular}{ c | c c c c c c c c c c c c c | c }
                                       & ceiling & floor & wall & beam & column & window & door & table & chair & sofa & bookcase & board & clutter & mIOU \\
            \hline
            Scratch                    &         &       &      &      &        &        &      &       &       &      &          &       &         &      \\
            \hline
            PointContrast              &         &       &      &      &        &        &      &       &       &      &          &       &         &      \\
            Contrastive Scene Contexts &         &       &      &      &        &        &      &       &       &      &          &       &         &      \\
            CME \textbf{(Ours)}        &         &       &      &      &        &        &      &       &       &      &          &       &         &      \\
        \end{tabular}
    }
    \caption{KITTI Semantic Segmentation results (mIOU)}
    \label{table:kittiSemanticResults}
\end{table*}

>>>>

\begin{table*}[t!]
    \centering
    \resizebox{\textwidth}{!}{
        \begin{tabular}{ c | c c c c c c c c c c c c c | c }
                                                      & ceiling        & floor          & wall           & beam           & column         & window         & door           & table          & chair          & sofa           & bookcase       & board          & clutter        & mIOU                   \\
            \hline
            Scratch                                   & 90.34          & \textbf{96.84} & 80.63          & 0              & 25.5           & 56.95          & 62.93          & 75.14          & 86.21          & 65.77          & 72.12          & 76.91          & 56.4           & 65.06                  \\
            Supervised                                & \textbf{91.81} & 96.74          & \textbf{84.11} & \textbf{0.21}  & \textbf{34.68} & \textbf{57.64} & \textbf{81.53} & \textbf{77.63} & \textbf{89.82} & \textbf{85.76} & \textbf{76.03} & \textbf{79.27} & \textbf{57.67} & \textbf{70.22} (+5.16) \\
            \hline
            PointContrast                             & 91.97          & \textbf{96.67} & 82.4           & 0              & 17.84          & 56.49          & \textbf{75.39} & \textbf{77.63} & 87.35          & 63.3           & 73.53          & \textbf{79.55} & 58.76          & 66.22 (+1.16)          \\
            PointContrast - Same Scan                 & 91.03          & 96.27          & \textbf{82.8}  & 0              & 31.53          & 57.27          & 69.33          & 76.97          & \textbf{88.83} & 45.49          & 71.02          & 77.09          & 57.06          & 64.97 (-0.09)          \\
            PointContrast - 70\% overlap              & 91.85          & 96.56          & 83.55          & 0              & 28.25          & 59.36          & 73.53          & 78.51          & 88.28          & 79.95          & 74.61          & 76             & 61.08          & 68.58 (+3.52)          \\
            Contrastive Scene Contexts                & \textbf{92.34} & 96.02          & 83.53          & 0              & \textbf{40.88} & \textbf{57.73} & 72.11          & 77.5           & 88.15          & \textbf{74.61} & \textbf{74.52} & 76.45          & \textbf{62.64} & 68.96 (+3.9)           \\
            Contrastive Scene Contexts - Same Scan    & 91.68          & 96.59          & 83.21          & 0              & 40.38          & 58.12          & 70.42          & 76.77          & 87.13          & 69.33          & 68.77          & 82.34          & 58.45          & 67.94 (+2.88)          \\
            Contrastive Scene Contexts - 70\% overlap & 92.68          & 96.63          & 83.99          & 0              & 42.37          & 55.95          & 77.17          & 75.74          & 89.57          & 82.74          & 73.45          & 80.67          & 60.55          & \textbf{70.12} (+5.06) \\
            CME \textbf{(Ours)}                       & 90.8           & 96.57          & 82.52          & \textbf{0.110} & 30.94          & 56.94          & 68.71          & 75.12          & 88.48          & 71.7           & 72.17          & 73.783         & 56.35          & 66.48 (+1.42)          \\
        \end{tabular}
    }
    \caption{S3DIS Semantic Segmentation results (mIOU)}
    \label{table:s3disResults}
\end{table*}

\begin{table*}[t!]
    \centering
    \resizebox{0.8\textwidth}{!}{
        \begin{tabular}{ c | c c c c c c c c c c | c }
                                                      & beam & column        & window        & door & table         & chair         & sofa          & bookcase      & board         & clutter       & mAP@0.5              \\
            \hline
            Scratch                                   & 0    & 12.8          & 61.7          & 92.0 & 51.4          & 87.3          & 62.4          & 38.5          & 87.0          & 37.1          & 53.0                 \\
            Supervised                                & 0    & 26.0          & 74.3          & 84.5 & 43.3          & 87.3          & \textbf{81.8} & 37.4          & \textbf{85.4} & \textbf{41.2} & \textbf{56.2} (+3.2) \\
            \hline
            PointContrast                             & 0    & 24.7          & 67.9          & 90.7 & 43.8          & 92.0          & 72.7          & 32.3          & 85.6          & 38.0          & 54.8 (+1.8)          \\
            PointContrast - Same Scan                 & 0    & 19.8          & 70.7          & 92.1 & 48.4          & 90.5          & 81.8          & 38.4          & 90.4          & 34.1          & 56.6 (+3.6)          \\
            PointContrast - 70\% overlap              & 0    & 22.6          & 71.6          & 94.6 & 45.8          & 87.9          & 71.7          & 37.0          & 81.0          & 40.9          & 55.3 (+2.3)          \\
            Contrastive Scene Contexts                & 0    & 32.9          & 69.2          & 93.0 & 47.6          & 87.5          & 80.9          & 39.6          & 87.5          & 40.4          & 57.8 (+4.8)          \\
            Contrastive Scene Contexts - Same Scan    & 0    & 32.0          & 69.3          & 96.1 & 38.7          & 89.4          & 87.6          & 38.8          & 81.3          & 38.8          & 57.2 (+4.2)          \\
            Contrastive Scene Contexts - 70\% overlap & 0    & 27.2          & 76.9          & 95.4 & 42.2          & 90.3          & 90.9          & 42.6          & 84.7          & 38.7          & \textbf{58.9} (+5.9) \\
            CME \textbf{(Ours)}                       & 0    & \textbf{35.0} & \textbf{70.0} & 83.4 & \textbf{53.9} & \textbf{88.9} & 71.7          & \textbf{42.2} & 76.1          & 36.7          & 55.8 (+2.8)          \\
        \end{tabular}
    }
    \caption{S3DIS Instance Segmentation Results (mAP@0.5)}
    \label{table:s3disInstanceSegmention}
\end{table*}

@@

\begin{table*}[t!]
    \centering
    \resizebox{0.3\textwidth}{!}{
        \begin{tabular}{ c | c }
                                       & mIOU  \\
            \hline
            Scratch                    & 41.82 \\
            \hline
            PointContrast              & 38.67 \\
            Contrastive Scene Contexts & 41.12 \\
            CME \textbf{(Ours)}        & 40.37 \\
        \end{tabular}
    }
    \caption{KITTI Semantic Segmentation results (mIOU)}
    \label{table:kittiSemanticResults}
\end{table*}
